Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-07 WSSSPE3/report/WSSSPE3_review.tex
minor change - formatting
removing number of groups in intro

This report is based on collaborative notes taken with during the workshop,
which were linked from the GitHub issues that represented the potential and
actual working
groups\footnote{\url{https://github.com/issues?q=label\%3A\%22WSSSPE3+activity\%22}}.
Overall, the report discusses the organization work done before the workshop
(\S\ref{sec:preworkshop}); the keynotes (\S\ref{sec:keynote}); a series of
lightning talks (\S\ref{sec:lightning}), intended to give an opportunity for
attendees to quickly highlight an important issue or a potential solution. The
report also gives summaries of action plans proposed by the eleven working
groups (\S\ref{sec:WGs}), and some conclusions (\S\ref{sec:conclusions}).
Lists of the organizing committee (Appendix~\ref{sec:orgcom}), the registered
attendees (Appendix~\ref{sec:attendees}), and the travel award recipients
(Appendix~\ref{sec:awardees}) are provided. Finally, the report includes longer
descriptions of the activities that
occurred in each of the working groups that made substantial progress 
(Appendices~\ref{sec:appendix_best_practices}--\ref{sec:appendix_user_community}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynote \note{Lead: S.-C. Choi.  See \href{http://tinyurl.com/qbbqgsj}{slides} \& \href{http://tinyurl.com/q45kfcn}{video}.}} \label{sec:keynote} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lightning Talks} \label{sec:lightning}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{need to update for WSSSPE3}
\todo{KEN: Should these be bolded? - dsk: yes, titles can be bolded, but contents under each should not}
\begin{comment}
\note{
\href{http://wssspe.researchcomputing.org.uk/wssspe3/agenda/}{Slides.}}
\end{comment}

>>>>

This report is based on collaborative notes taken with during the workshop,
which were linked from the GitHub issues that represented the potential and
actual working
groups\footnote{\url{https://github.com/issues?q=label\%3A\%22WSSSPE3+activity\%22}}.
Overall, the report discusses the organization work done before the workshop
(\S\ref{sec:preworkshop}); the keynotes (\S\ref{sec:keynote}); a series of
lightning talks (\S\ref{sec:lightning}), intended to give an opportunity for
attendees to quickly highlight an important issue or a potential solution. The
report also gives summaries of action plans proposed by the working
groups (\S\ref{sec:WGs}), and some conclusions (\S\ref{sec:conclusions}).
Lists of the organizing committee (Appendix~\ref{sec:orgcom}), the registered
attendees (Appendix~\ref{sec:attendees}), and the travel award recipients
(Appendix~\ref{sec:awardees}) are provided. Finally, the report includes longer
descriptions of the activities that
occurred in each of the working groups that made substantial progress 
(Appendices~\ref{sec:appendix_best_practices}--\ref{sec:appendix_user_community}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynote \label{sec:keynote}}
%\note{Lead: S.-C. Choi.  See \href{http://tinyurl.com/qbbqgsj}{slides} \& \href{http://tinyurl.com/q45kfcn}{video}.}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lightning Talks} \label{sec:lightning}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}
\note{
\href{http://wssspe.researchcomputing.org.uk/wssspe3/agenda/}{Slides.}}
\end{comment}
